Design of Blur Invariant Fiducial for Low Cost Quadcopter

### 2014-03-01 ECCV/paper.tex
Added comparison with BLUT as well as with PiTag

\section{Fiducial Detection Algorithm}
\begin{figure}
\includegraphics[width=\linewidth]{overall_flow.pdf}
\caption{Overall Workflow}
\end{figure}
Our fiducial detection strategy is different from \cite{NaimarkF02} and works
under significant amount of blur. Our algorithm is based on the fact that there
is no blur in the direction perpendicular to the direction of the motion.
Overall flow of fiducial detection algorithm can be summarised as follows:
\begin{itemize}
  \item Apply Gabor Filter on input image
  \item Find Connected components in Gabor output
  \item Cluster the connected components in bounding box
  \item Detect code in the bounding box
  \begin{itemize}
    \item Run PCA on Gabor output in bounding box
    \item Find intensity profile along first principal component passing through
    centroid
    \item If there are less than four black to white transitions in the
    intensity profile, ignore the bouding box
    \item Otherwise, classify the detected code by the classifer trained on
    standards.
  \end{itemize}
\end{itemize}

@@

\subsection{Comparison}
We will compare our results with standard fiducials such as ARTag. Also, we will
compare our results with Blur driven tracker.
\subsubsection{Comparison with ARTag}
\subsubsection{Comparison with Blut}

>>>>

\section{Fiducial Detection Algorithm}

We have performed blur simulation experiment on Pi-tag \cite{Pitag13} to find
how blur effects circular patterns. We tried to detect blurred Pi-tag using
\cite{ros_pitag}.

\begin{figure}
\begin{subfigure}[b]{0.3\textwidth}
  \centering
  \includegraphics[width=\linewidth]{detect_noblur.jpg}
  No Blur  
 \end{subfigure}
 \begin{subfigure}[b]{0.3\textwidth}
  \centering
  \includegraphics[width=\linewidth]{detect_blur15.jpg}
  Blur Scale = 15  
 \end{subfigure}
 \begin{subfigure}[b]{0.3\textwidth}
  \centering
  \includegraphics[width=\linewidth]{nodetect_blur20.jpg}
  Blur Scale = 20  
 \end{subfigure}
 \caption{Effect of blur on detection of Pi-Tag}
 \label{fig:pitag_blur}
\end{figure}

From Fig. \ref{fig:pitag_blur}, it can be seen that, Pi-tag detection
fails when blur scale is more than 15. The reason behind this is, Pi-tag
detection is based on Ellipse detection which will fail in the presence of
significant amount of blur. So, ellipse detection may not be the efficient way
to detect circular patterns under blur.

\begin{figure}
\includegraphics[width=\linewidth]{overall_flow.pdf}
\caption{Overall Workflow}
\end{figure}

Our fiducial detection strategy is different from \cite{NaimarkF02}\cite{Pitag13} and
works under significant amount of blur. Our algorithm is based on the fact that there
is no blur in the direction perpendicular to the direction of the motion.
Overall flow of fiducial detection algorithm can be summarised as follows:

\begin{itemize}
  \item Apply Gabor Filter on input image
  \item Find Connected components in Gabor output
  \item Cluster the connected components in bounding box
  \item Detect code in the bounding box
  \begin{itemize}
    \item Run PCA on Gabor output in bounding box
    \item Find intensity profile along first principal component passing through
    centroid
    \item If there are less than four black to white transitions in the
    intensity profile, ignore the bouding box
    \item Otherwise, classify the detected code by the classifer trained on
    standards.
  \end{itemize}
\end{itemize}

@@

\subsection{Comparison}
We will compare our results with standard fiducials such as ARTag. Also, we will
compare our results with Blur driven tracker(BLUT)\cite{Wu:2011}.
\subsubsection{Comparison with ARTag}

\subsubsection{Comparison with BLUT} 
We have used sample image sequence to test the performance of BLUT\cite{Wu:2011}
and compare it with out result on the same image sequence. From Fig. \ref{fig:BLUT_output},
it can be inferred that BLUT is able to track the fiducial when the position of
fiducial doesnot change too much in successive frames. Also, it can be seen
that, once BLUT looses the track of the fiducial, it is not able to recover from
that. But, our algorithm is able to track the fiducial irrespecive of the change
in the position of the fiducial in the image as shown in Fig.
\ref{fig:our_output}.

\begin{figure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{11.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{12.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{13.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{14.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{15.jpg}
\end{subfigure}
\caption{Output of BlUT on sample image sequence}
\label{fig:BLUT_output}
\end{figure}

\begin{figure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{output11.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{output12.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{output13.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{output14.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{output15.jpg}
\end{subfigure}
\caption{Output of our algorithm on image sequence used in
Fig. \ref{fig:BLUT_output}}
\label{fig:our_output}
\end{figure}
